---
title: "Homework 4"
output: html_document
date: "2022-10-31"
---

```{r}
p<-read.csv("~/downloads/Pharmaceuticals.csv",header = TRUE)
head(p)
```
```{r}
p1 <- p[,3:11]
head(p1)
ps <- scale(p1)
head(ps)
```
```{r}
wss <- (nrow(ps)-1)*sum(apply(ps,2,var))
wss
```
```{r}
for (i in 2:15) wss[i] <- sum(kmeans(ps,centers=i)$withinss)
wss
```
```{r}
plot(1:15, wss, type="b", xlab="Number of Clusters",ylab="Within groups sum of squares")
```
```{r}
fit <- kmeans(ps, 5)
```
```{r}
aggregate(ps,by=list(fit$cluster),FUN=mean)
```
```{r}
ps1 <- data.frame(ps, fit$cluster)
ps1
```
```{r}
library(cluster)
clusplot(ps, fit$cluster, color=TRUE, shade=TRUE, labels=2, lines=0)
```
#b
#Cluster 1 - Row 1,3,4,5,19,20
#Cluster 2 - Row 2,6,18
#Cluster 3 - Row 11,13,15,17
#Cluster 4 - Row 7,10,16,21
#Cluster 5 - Row 8,9,12,14

#Cluster 1 has lowest Leverage.
#Cluster 2 has highest PE ratio, lowest ROE, lowest ROA, lowest Asset Turnover, lowest Net Profit Margin
#Cluster 3 has highest Market Cap, highest ROE, highest ROA, highest Asset Turnover
#Cluster 4 has highest Net Profit Margin, lowest Beta, lowest PE Ratio, lowest Rev growth.
#Cluster 5 has highest Beta, highest Leverage, highest Rev growth and lowest Market Cap.

#c
#there is a pattern in clusters, it is in view of media recommendation variable. Cluster 3 does not have any sell media recommendation. Cluster 2 has mostly hold recommendation while cluster 4 also has mostly hold recommendation

#d
#Cluster 1 - Lowest Leverage cluster
#Cluster 2 - High PE ratio, Low ROE, ROA, Asset Turnover, Net Profit Margin Cluster
#Cluster 3 - High Market Cap, ROE, ROA, Asset Turnover cluster
#Cluster 4 - High Net Profit Margin, Low Beta, PE Ratio, Rev growth cluster
#Cluster 5 - High Beta, Leverage, Rev growth and Low Market Cap cluster